### 2020-03-27 probabilisticProgrammingMartingales.tex
Add alternative semantics
Draft description of a different version of sampling semantics more
compatible with variable reduction order.

>>>>

\subsection{Alternative Semantics}
\akr{This version of the semantics is much more convenient for allowing multiple different reduction orders. I don't currently have a proof of the equivalence of this with the more usual semantics. I expect that that would be somewhat complicated, but not terribly difficult. I don't know whether a semantics like this has already been defined elsewhere. I just thought I'd write it out so you can see it and in case I use it later. If I do end up actually using it I'll write it up nicer, but hopefully this is at least enough for you to understand what I mean.}

Given a term $M$, let $L(M)$ be the set of occurrences in $M$ of variables, $\tsample$ and $\tY$, and let $F(M)$ be the free magma on $L(M)$. \akr{Only the elements with no \tsample{}s except in the rightmost position are used. I'm not sure whether making this explicit in the definition of $F(M)$ makes things more or less clear.} Let $I = [0,1]$ and $S = I^{F(M)}$, with the Borel $\sigma$-algebra and the product measure.

For any reduction \akr{including reductions not included in the definition above, i.e.~out of order reductions} $M \to N$, define a corresponding map $F(M \to N) : F(N) \to F(M)$ induced (as a magma morphism) by the obvious injection along with the replacements
\begin{align*}
F(E[(\lambda x. F[x_i])G[y]] \to E[F(G[y]/x)[G[y_i]]]) (x_i \cdot y) & = y_i\\
F(E[\tY_i F[y]] \to E[F[y_0] (\tY F[y])]) (y_0) & = \tY_i \cdot y
\end{align*}
where $y$ can be any of the things in $L(N)$.

The one-step reduction is given by the function $\red : \Lambda \times S \to \Lambda \times S$ where
\begin{equation}
\red(M,s) = \left\{
    \begin{array}{ll}
        (E[N],s \circ F(E[R] \to E[N])) & \text{if } M = E[R], R \to N \text{ and } R \neq \tsample \\
        (E[\underline{s(\tsample_i)}],s\mid_{F(E[\underline{s(\tsample_i)}])}) & \text{if } M = E[\tsample_i] \\
        (M,s) & \text{if } M \text{ normal form}
    \end{array} \right .
\end{equation}

Essentially the entropy value here contains a pre-selected random value for each possible \tsample-reduction, in a way independent of reduction order, taking into account the possible duplication of \tsample{}s in $\beta$- and \tY-reduction steps.
